On the Duality of Frequentist Point Estimates and Bayesian Shrinkage Priors: An Extension based on the Triple-Gamma-Prior

### 2024-03-11 01_latex/MScThesis_Econ.tex
Some test code on LASSO

\pagebreak
\section{Introduction}
\section{Theoretical Section}
\section{Simulation Section}

>>>>

\pagebreak
%----- Introduction -----
\section{Introduction}

%----- Literature Review -----
\section{Literature Review}
\subsection{Bayesian View}
\subsection{Frequentist View}
\subsection{Machine Learning Literature combating Model Complexity}

%----- Theoretical Section
\section{Theoretical Section}
\subsection{Model Complexity}
\subsection{Under- and Overfitting}
\subsubsection{Regularization}
\subsubsection{Shrinkage Priors}
\subsection{Duality of the Ridge Regression}
%----- Model Setup and Derivation
\section{Model Setup and Derivation}
Mathematical derivation of TGP into frequentist view?

%----- Simulation Section
\section{Simulation Section}
Use the earlier derivation, code up the functions and simulate data to check behaviour for different datasets. Compare to base OLS, Ridge and Lasso Regression?
\subsection{Computational Performance}
\subsection{Implementation as R Package?}

%----- Small Applied Section
\section{Small Applied Section}
Here I am planning to apply the TGP using Peter's Bayesian Package and the self coded frequentist code on a small dataset.
\section{Conclusion}
\section{Possible Extensions and Criticism}
\section{References}
